Persistence in functional topology and a correction to a theorem of Morse

### 2021-07-26 introduction.tex
Remove unused commands

While Morse's work on functional topology did not have a long lasting impact on minimal surface theory or the calculus of variations in general ---possibly because, as Hildebrandt [4, p. 324] puts it, ``Morse--Tompkins' original paper [is] unreadable and inaccessible for the non-specialist''---
many of his ideas have resurfaced and flourished in other domains.
In particular, in applied topology and topological data analysis, several key insights of Morse have been independently rediscovered as part of the development of \emph{persistent homology}, a technique that provides robust and efficiently computable invariants of filtered spaces using the functorial properties of homology.
Its success in applied topology has motivated a refined abstract theory of persistence that lies on the intersection of geometry, topology, and representation theory.

>>>>

While Morse's work on functional topology did not have a long lasting impact on minimal surface theory or the calculus of variations in general ---possibly in part because, as Hildebrandt [4, p. 324] puts it, ``Morse--Tompkins' original paper [is] unreadable and inaccessible for the non-specialist''---
many of his ideas have resurfaced and flourished in other domains.
In particular, in applied topology and topological data analysis, several key insights of Morse have been independently rediscovered as part of the development of \emph{persistent homology}, a technique that provides robust and efficiently computable invariants of filtered spaces using the functorial properties of homology.
Its success in applied topology has motivated a refined abstract theory of persistence that lies on the intersection of geometry, topology, and representation theory.
